---
title: "Homework 9"
output:
  html_notebook: default
  pdf_document: default
---
6210422036: Tanat Iempreedee  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=TRUE}
library(ggplot2)
library(fpp2)
library(forecast)
library(GGally)

data <- read.table('c5p9.csv',sep=',',header=TRUE)
data
```

## Correlations

```{r}
ggpairs(data, columns=2:4)
```
## Fit linear regression
```{r}
reg <- lm(AS~INC+POP, data=data)
summary(reg)
```
### 1) Estimate values for $b_0, b_1, b_2$ for model

- $\beta_0 = -307500$  
- $\beta_1 = 14.56$  
- $\beta_2 = 1397$  

$AS = -307500 + 14.56(INC) + 1397(POP)$  


### 2) Are the signs you find for the coefficients consistent with your expectations?
Both coefficients for INC and POP are positive  
- Area with higher income should have a higher sales  
- Also, greater population should increase the sales

### 3) Are the coefficients for the two explanatory variables significantly different from zero?

- **INC**: $\beta_1$ is significantly different from zero but at significance level of 0.9  
- **POP**: $\beta_2$ is significantly different from zero 

### 4) What percentage of the variation in AS is explained by this model

**R-squared = 0.9295**  

This model can explain the variation in AS by 92.95%


### 5) What point estimate of AS would you make for a city where INC=23175 and POP=128.07? Also find the 95% prediction interval
```{r}
newX <- data.frame(INC=23175, POP=128.07)
forecast(reg, newdata = newX)
```

- Point estimate = 208,811.3
- Prediction interval = [74308.43, 343314.2]



