---
title: "Homework 11"
output: html_notebook
---
6210422036: Tanat Iempreedee  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp2)
library(forecast)
library(ggplot2)
library(dplyr)

da <- read.table("Advert.txt", header=TRUE, colClasses=c('numeric','factor','numeric'))
str(da)
```
## EDA
```{r}
cor(da$advert, da$sales)
```

```{r}
ggplot(data=da, aes(x=advert, y=sales)) +
  geom_point() + 
  xlab('Advert') + ylab('Sales')
```
## Transform
```{r}
# Transform
da <- da %>% mutate(advert_sq=advert^2) %>%
  mutate(advert_log=log(advert)) %>% 
  mutate(sales_log=log(sales))
head(da)
```
```{r}
cor(da$advert_log, da$sales_log)
```
## Model 1: Log-Log
```{r}
# Model1: log-log
reg1 <- lm(sales_log ~ advert_log, data=da)
summary(reg1)
AIC(reg1)
CV(reg1)
```
```{r}
ggplot(data=da, aes(x=advert_log, y=sales_log)) +
  geom_point() +
  geom_line(aes(y=fitted(reg1)), size=1, color='red') +
  xlab("Log(Advert)") + ylab("Log(Sales)")
```
### Coefficient Interpretation - Log-log
  
$ln(Sales) = 6.39213 + 0.09529 ln(Advert)$  
$\beta_1 = 0.09529$

1% increase in Advert -> 0.09% increase in Sales

## Model 2: Quadratic
```{r}
# Model2: Quadratic
reg2 <- lm(sales ~ advert + advert_sq, data=da)
summary(reg2)
AIC(reg2)
CV(reg2)
```
```{r}
ggplot(data=da, aes(x=advert, y=sales)) +
  geom_point() +
  geom_line(aes(y=exp(fitted(reg1)),color='red'), size=1) +
  geom_line(aes(y=fitted(reg2), color='blue'), size=1) +
  xlab('Advert') + ylab('Sales') +
  scale_color_identity(name = "Model fit",
                     breaks = c("red", "blue"),
                     labels = c("Log-Log", "Quadratic"),
                     guide = "legend")
```
## Choose between log-log and quadratic

#### Compare Cross Validation Result
```{r}
rbind(LOGLOG=CV(reg1), QUADRATIC=CV(reg2))
```
#### Interpretation
Choose **Log-log** model which gives the lower AIC, even though Quadratic gives the better Adjusted R Squared.  
From the problem context, increasing advertisement expenditure should not decrease Sales. Instead, the growth of Sales could saturate at some point which aligns more with logarithmic trend.

#### Solution
We can't use CV and AIC/AICc/BIC which base on MLE to compare log-log and quadratic. Since it's log(y) vs y. We choose the right model from AdjR2.
