---
title: "Homework 10"
output:
  html_notebook: default
---

6210422036: Tanat Iempreedee  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp2)
library(forecast)

d <- read.table('c3t13.txt', header=TRUE,
                colClasses = c('numeric','factor'))
str(d)
```
```{r}
dts <- ts(data=d, frequency=12, start=c(2015,4))
autoplot(dts[,'Mustard']) +
  ylab('Sales')
```
#### Prepare data to forecast
```{r}
newdata <- data.frame(trend=28:33, 
                      season=factor(7:12, levels=1:12),
                      fevent=factor(rep(1,6), levels=1:3))
newdata
```

## Model 1: Mustard ~ trend
```{r}
# Model 1
reg1 <- tslm(Mustard ~ trend, data=dts)
summary(reg1)

fc <- forecast(reg1, newdata=newdata)
autoplot(dts[,'Mustard'], series='Data') +
  autolayer(fitted(reg1), series='Fitted') +
  autolayer(fc, series='Forecast') +
  ylab('Sales') +
  ggtitle('Mustard ~ trend')
```

## Model 2: Mustard ~ trend + season + Event
```{r}
# Model 2
fevent <- factor(dts[,'Event'], levels=1:3)

reg2 <- tslm(Mustard ~ trend + season + fevent, data=dts)
summary(reg2)

fc <- forecast(reg2, newdata=newdata)
autoplot(dts[,'Mustard'], series='Data') +
  autolayer(fitted(reg2), series='Fitted') + 
  autolayer(fc, series='Forecast') +
  ylab('Sales') +
  ggtitle('Mustard ~ trend + season + fevent')

```
## Model 3: Mustard ~ trend + season
```{r}
reg3 <- tslm(Mustard ~ trend + season, data=dts)
summary(reg3)

fc <- forecast(reg3, newdata=newdata)
autoplot(dts[,'Mustard'], series='Data') +
  autolayer(fitted(reg3), series='Fitted') +
  autolayer(fc, series='Forecast') + 
  ylab('Sales') +
  ggtitle('Mustard ~ trend + season')
```

## Model 4: Mustard ~ trend + Event
```{r}
reg4 <- tslm(Mustard ~ trend + fevent, data=dts)
summary(reg4)

fc <- forecast(reg4, newdata=newdata)
autoplot(dts[,'Mustard'], series='Data') +
  autolayer(fitted(reg4), series='Fitted') +
  autolayer(fc, series='Forecast') +
  ylab('Sales') +
  ggtitle('Mustard ~ trend + fevent')
```
## Compare AIC
Based on the AIC, Model 2 is selected.
```{r}
data.frame(MD1=AIC(reg1),MD2=AIC(reg2),MD3=AIC(reg3),MD4=AIC(reg4))
```
## Forecast
```{r}
fc <- forecast(reg2, newdata=newdata)
fc
```
## Question
If we want to optimize the campaign spending, what are other possible independent variables? Indicate whether they are numerical or categorical.

- Campaign Spending (numerical) plan for each month
- A flag indicate Campaign sensitivity (categorical)?
- If $Profit = Sales - Qty(UnitCost) - CampaignSpending - ...$, Unit cost could affect finding an optimum campaign spending as well, we may want to use costs as well, e.g., estimated raw material cost (numerical) for each month?


