---
title: "Homework 02"
output:
  html_notebook: default
  pdf_document: default
---

## 1. Chapter 1 Problem 8 (c1p8): Use R

```{r echo=TRUE}
library(xlsx)

data <- read.xlsx('c1p8_2.xlsx','Sheet1', header=TRUE)

y <- ts(data$RetailStoreSales, frequency=1)
y
```

```{r echo=TRUE}
autoplot(y) + 
  ggtitle("Retail Store Sales") +
  xlab("Year") +
  ylab("Amount")
```

```{r echo=TRUE, warning=FALSE}
yfitN <- naive(y, h=1)

ypred <- ts(c(yfitN$fitted, yfitN$mean))

autoplot(y, series='Actual') +
  autolayer(ypred, series="Naive") + 
  xlab("Year") + ylab("Amount") +
  ggtitle("Naive Forecasts for Retail Store Sales")
```
```{r echo=TRUE}
accuracy(yfitN)
```
## 2. Integrative Case: The Gap KW pp.81-83

```{r echo=TRUE}
data <- read.xlsx('C2 Gap Sales Data_2.xlsx','Quarterly Gap Sales Data', header=TRUE)
data
```
```{r echo=TRUE}
y <- ts(data$GapSales, frequency=4, start=c(2006, 01))
y
```

#### 1. Calculate the mean and standard deviation for the set of quarterly data in 2016. Also compute coefficient of variation

```{r echo=TRUE}
y2016 <- tail(y, 4)
y2016
```

```{r echo=TRUE}
paste('mean:',mean(y2016))
paste('sd:  ',sd(y2016))
paste('cv:  ',sd(y2016)/mean(y))
```
#### 2. Plot these data in a time-series plot.

```{r echo=TRUE}
autoplot(y) + 
  ggtitle("Gap Sales ($M)") +
  xlab("Quarter") +
  ylab("Amount ($M)")
```
#### 3. Using data for 2006Q1 through 2016Q4, construct the correlogram for lags of 1 through 12
```{r echo=TRUE}
ggAcf(y, 12)

```
Seasonal = Yes  
Trend = Not sure

```{r echo=TRUE}
ggseasonplot(y, year.labels = TRUE, year.labels.left = TRUE) +
  ylab("Millions") +
  ggtitle("Seasonal plot")

```
#### 4. What forecasting methods might you suggest if you were to forecast the Gap's quarterly sales?

##### Train/Test Split
```{r echo=TRUE}
ytrain <- window(y, start=c(2006,1), end=c(2014,4))
ytest <- window(y, start=c(2015,1), end=c(2016,4))
autoplot(y) +
  autolayer(ytrain, series="Training") +
  autolayer(ytest, series="Test")
```
```{r echo=TRUE}
yfitSN <- snaive(ytrain, h=8)
accuracy(yfitSN, ytest)
yfitETS <- forecast(ytrain, h=8)
accuracy(yfitETS, ytest)
yfitHW <- hw(ytrain, h=8)
accuracy(yfitHW, ytest)
```

```{r echo=TRUE}
autoplot(y) +
  autolayer(yfitSN, series="Seasonal Naive", PI=FALSE) + 
  autolayer(yfitETS, series="ETS", PI=FALSE) +
  autolayer(yfitHW, series="Holt-Winters", PI=FALSE) +
  xlab("Year") + ylab("Sales Amount ($M)") +
  ggtitle("Forecasts for Gap Sales") +
  guides(colour=guide_legend(title="Forecast"))
```

