---
title: "Homework 12"
output: html_notebook
---
6210422036: Tanat Iempreedee  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(caret)
library(e1071)
library(reshape2)

d <- read.table('shipment.csv', sep=',', header=TRUE,
                colClasses=c('factor','numeric','numeric','factor'))
str(d)
```
## 1) EDA

Among all late shipments, the average distance and weight are higher than on-time shipments.
```{r}
d %>% group_by(Late) %>%
  summarise(AvgDistance=mean(Distance), AvgWeight=mean(Weight), n=n())
```

```{r}
# EDA
ggplot(d, aes(Distance, Weight)) +
  geom_point(aes(color=Late)) +
  facet_wrap(~LSPRank) +
  scale_color_brewer(palette="Set2")
```
```{r}
# count plot
ggplot(d, aes(fill=Late, x=LSPRank)) + 
  geom_bar(position="dodge") +
  scale_fill_brewer(palette="Set2")
```
```{r}
# normalized count plot
d %>% group_by(LSPRank) %>% 
  summarise(Late.N=mean(Late=='0'),Late.Y=mean(Late=='1')) %>%
  melt(variable.name='Late.p') %>%
  ggplot(aes(x=LSPRank, y=value, fill=Late.p)) +
    geom_bar(position='stack', stat='identity') +
    ylab('Late Proportion') +
    scale_fill_brewer(palette="Set2")
```
## 2) Fit Logistic Regression
```{r}
logreg <- glm(Late~Distance + Weight + LSPRank, data=d, family="binomial")
summary(logreg)
```
### Coefficient interpretation
- Increases in **Distance** and **Weight** raises the odds of being late. and Weight has a higher effect. -> make sense
- **LSPRank** of 2,3,4 has less probability of being Late compared to LSPRank 1. The higher ranks of LSPRank decreases the  odds of being late. This seems to make sense if higher rank means higher quality of a service provider.  


## 3) Predict
```{r}
newdata <- data.frame(Distance=680,Weight=3.7,LSPRank=factor(2, levels=1:4))
newdata
```

```{r}
y_pred <- predict(logreg, newdata=newdata ,type='response')
y_pred
ifelse(y_pred >= 0.5, 'Late', 'Not Late')
```

