---
title: "Homework 5"
output: html_notebook
---
6210422036: Tanat Iempreedee  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset
```{r init}
library(ggplot2)
library(fpp2)
library(forecast)
library(seasonal)

src <- read.table('c6p14.csv', sep=',', header=TRUE)
data <- ts(src$CS, frequency=4, start=c(1996,1))
data
```
### Test set
```{r}
ytest <- ts(c(301.1,336.7,341.8,293.5), frequency=4, start=(c(2017,1)))
ytest
```
```{r}
ylabel <- 'Car sales'
title <- 'Car sales in the upper mid-west'
autoplot(data, series='Data') +
  autolayer(ytest, series='Test') +
  ylab(ylabel) + ggtitle(title)
```
## STL Decomposition
```{r}
mSTL <- mstl(data)
autoplot(mSTL)
```
### Seasonally Adjusted
```{r}
sa <- seasadj(mSTL)
autoplot(data, series="Data") +
  autolayer(sa, series="Seasonally Adjusted") 
```

#### Getting the seasonal indices from the latest year

```{r}
siLast <- tail(seasonal(mSTL),n=4)
siLast
```
Since the SI is bound to the historical time period. In order to use it to re-seasonalize the predicted values, we have to make it a plain numerical vector, or else getting an error.
```{r}
siLast <- as.numeric(siLast)
siLast
```

## 1) Naive

```{r naive}
# forecast using Naive
saNaive <- naive(sa,h=4)
autoplot(saNaive)
```
#### Naive - actual forecast
```{r}
ypredNaive <- saNaive$mean + siLast
ypredNaive
```
```{r}
autoplot(data, series='Data') +
  autolayer(ytest, series='Test') +
  autolayer(saNaive$fitted + seasonal(mSTL), series='Fitted') + 
  autolayer(ypredNaive, series='Forecast') +
  ylab(ylabel) + ggtitle('STL + Naive')
```

```{r}
accuracy(ypredNaive, ytest)
```
### 2) Holt

```{r holt}
saHolt <- holt(sa, h=4)
autoplot(saHolt)
```
#### Holt - actual forecast
```{r}
ypredHolt <- saHolt$mean + siLast
ypredHolt
```


```{r}
autoplot(data, series='Data') +
  autolayer(ytest, series='Test') + 
  autolayer(saHolt$fitted + seasonal(mSTL), series='Fitted') +
  autolayer(ypredHolt, series='Forecast') +
  ylab(ylabel) + ggtitle('STL + Holt')
```
```{r}
accuracy(ypredHolt, ytest)
```
## 3) ETS (Auto)
```{r ets}
ets_model1 <- ets(sa)
summary(ets_model1)
```
```{r}
checkresiduals(ets_model1)
```
```{r echo=TRUE}
ypredETS1 <- forecast(ets_model1, h=4)$mean + siLast
ypredETS1
```
```{r}
autoplot(data, series='Data') +
  autolayer(ytest, series='Test') +
  autolayer(fitted(ets_model1) + seasonal(mSTL), series='Fitted') +
  autolayer(ypredETS1, series='Forecast') +
  ylab(ylabel) + ggtitle('STL + ETS (A,N,N)')
```
```{r}
accuracy(ypredETS1, ytest)
```
## 4) ETS (M,A,N)
```{r ets2}
ets_model2 <- ets(sa, 'ZAN')
summary(ets_model2)
```
```{r}
checkresiduals(ets_model2)
```
```{r}
ypredETS2 <- forecast(ets_model2, h=4)$mean + siLast
ypredETS2
```
```{r}
autoplot(data, series='Data') +
  autolayer(ytest, series='Test') +
  autolayer(fitted(ets_model2) + seasonal(mSTL), series='Fitted') +
  autolayer(ypredETS2, series='Forecast') +
  ylab(ylabel) + ggtitle('STL + ETS (M,A,N)')
```
```{r}
accuracy(ypredETS2, ytest)
```
