---
title: "Homework 4"
output: html_notebook
---
6210422036 Tanat Iempreedee

```{r echo=TRUE}
library(ggplot2)
library(fpp2)
library(forecast)

data <- read.table("c3p11.csv", header=TRUE, sep = ',', fileEncoding = 'UTF-8-BOM')
data
```
## Creating Time-series
```{r echo=TRUE}
y <- ts(data$Sales, frequency=12, start=c(2002,1))
y
```

# A.

Plot the data to examine the possible existence of trend and seasonality in the data.

```{r}
autoplot(y) + ylab('Sales ($M)') + ggtitle('Full Service Retail Restaurant Sales ($M)')
```
```{r}
ggseasonplot(y, year.labels = TRUE, year.labels.left = TRUE) +
  ylab("Sales ($M)") +
  ggtitle("Seasonal plot")
```
- **Trend:** Yes, seems like linear.  
- **Seasonal:** Yes, A or M? We'll find out.  


## B.
Forecast using the 8 models below  
1. Simple exponential smoothing  
2. Holt's linear trend  
3. Damped trend  
4. Holt-Winters' additive seasonal  
5. Holt-Winters' multiplicative seasonl
6. Winters' additive seasonal with damped trend  
7. ETS (ZZZ)  
8. ETS (ZZZ, Damped=FALSE)  

### Train/Test split
```{r echo=TRUE}
ytrain <- window(y, start=c(2002,1), end=c(2013,12)) # train
ytest <- window(y, start=c(2014,1), end=c(2015,12)) # test 
autoplot(y) +
  autolayer(ytrain, series="Training") +
  autolayer(ytest, series="Test") +
  ylab("Sales ($M)") + ggtitle('Train/Test')
```
### 1) SES
```{r echo=TRUE}
ySES <- ses(ytrain, h=24)
accuracy(ySES, ytest)
```

```{r}
autoplot(ySES) + 
  autolayer(fitted(ySES), series="Fitted") +
  autolayer(ytest, series='Test') +
  ylab("Sales ($M)")
```
### 2) Holt's

```{r}
yHolt <- holt(ytrain, h=24)
accuracy(yHolt, ytest)
```
```{r}
autoplot(yHolt) + 
  autolayer(fitted(yHolt), series="Fitted") +
  autolayer(ytest, series='Test') +
  ylab("Sales ($M)")
```
### 3) Damped Holt's

```{r}
yHoltDamp <- holt(ytrain, h=24, damped=TRUE)
accuracy(yHoltDamp, ytest)
```
```{r}
autoplot(yHoltDamp) +
  autolayer(fitted(yHoltDamp), series='Fitted') +
  autolayer(ytest, series='Test') +
  ylab('Sales ($M)')
```

### 4) Holt-Winters' additive seasonal

```{r}
yHWA <- hw(ytrain, h=24, seasonal='additive')
accuracy(yHWA, ytest)
```
```{r}
autoplot(yHWA) +
  autolayer(fitted(yHWA), series='Fitted') +
  autolayer(ytest, series='Test') +
  ylab('Sales ($M)')
```

### 5) Holt-Winters' multiplicative seasonal

```{r}
yHWM <- hw(ytrain, h=24, seasonal='multiplicative')
accuracy(yHWM, ytest)
```
```{r}
autoplot(yHWM) +
  autolayer(fitted(yHWM), series='Fitted') +
  autolayer(ytest, series='Test') +
  ylab('Sales ($M)')
```
### 6) Damped Holt-Winters' additive
```{r}
yHWADamp <- hw(ytrain, h=24, damped=TRUE)
accuracy(yHWADamp,ytest)
```
```{r}
autoplot(yHWADamp) + 
  autolayer(fitted(yHWADamp), series='Fitted') +
  autolayer(ytest, series='Test') +
  ylab('Sales ($M)')
```
### 6) ETS (ZZZ)
```{r}
model1 <- ets(ytrain, "ZZZ")
summary(model1)
```
```{r}
autoplot(model1)
```
```{r}
checkresiduals(model1)
```

```{r}
m1pred <- forecast(model1, h=24)
accuracy(m1pred, ytest)
```

```{r}
autoplot(m1pred) +
  autolayer(fitted(m1pred), series='Fitted') + 
  autolayer(ytest, series='Test') +
  ylab('Sales ($M)')
```
### 7) ETS (ZZZ, Damped=FALSE)

```{r}
model2 <- ets(ytrain, "ZZZ", damped=FALSE)
summary(model2)
```

```{r}
autoplot(model2)
```

```{r}
checkresiduals(model2)
```

```{r}
m2pred <- forecast(model2, h=24)
accuracy(m2pred, ytest)
```
```{r}
autoplot(m2pred) +
  autolayer(fitted(m2pred), series='Fitted') + 
  autolayer(ytest, series='Test') +
  ylab('Sales ($M)')
```

## c. Model Comparison

Comparing MAPE of Train & Test for each model.
```{r}
metrics <- rbind(accuracy(ySES,ytest)[9:10],
                accuracy(yHolt,ytest)[9:10],
                accuracy(yHWA,ytest)[9:10],
                accuracy(yHoltDamp,ytest)[9:10],
                accuracy(yHWADamp,ytest)[9:10],
                accuracy(m1pred,ytest)[9:10],
                accuracy(m2pred,ytest)[9:10],
                accuracy(yHWM,ytest)[9:10])
metrics <- data.frame(metrics)
colnames(metrics) <- c("Train","Test")
rownames(metrics) <- c("SES","Holt","HW additive","Damped Holt","Damped HW additive", "ETS (M,Ad,M)","ETS (M,A,M)","HW multiplicative")
metrics[order(metrics$Test),]
```

### Summary
- **ETS(M,A,M)** as a result from ZZZ and Damped=FALSE parameters gives the lowest MAPE on Test set -> **[SELECTED]**  
- ETS(M,Ad,M) is from using ZZZ option. Even though its AICc = 2302.743 is lower compared to 2308.233 from ETS(M,A,M), its MAPE loses against many competitors here.  
- Trend seems to be linear as the Damped models yield lower performance compared to other linear trend models.
- Seasonal seems to align with multiplicative more by looking at the top 2 scorers.  



